AP/PA Tables ITHIM Global

### 2022-05-16 summary_tables_PA_AP.Rmd
Fix overwritten object and regen

cl <- list()
td <- NA
for (city in cities) {

@@

@@

@@

output_file <- "results/multi_city/AP/desc_stats.xlsx"
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         CO2_emissions = cl,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)

>>>>

co2_conc <- list()
td <- NA
for (city in cities) {

@@

  if (length(co2_conc) == 0)
    co2_conc <- td
  else
    co2_conc <- left_join(co2_conc, td)

@@

#cl$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling", "Public Transport")
co2_conc$Scenario <- c("Baseline", "Bicycling", "Driving", "Public Transport")

print(kable(co2_conc))

@@

output_file <- "results/multi_city/AP/desc_stats.xlsx"
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         CO2_conc = co2_conc,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)
